
---
title: "Mini-Project 02 - How Do You Do 'You Do You'?"
author: "jackeee101"
editor:
    mode: source
format:
    html:
        code-fold: true
---

```{r}
library(tidyverse)
library(glue)
library(readxl)
library(httr2)
library(ggplot2)
library(scales)
library(gt)
options(scipen = 999)
```

## Introduction

A suitable introduction goes here. In this mini-project, I intend to demonstrate
my skills at Combining Data/Data Visualization in an analysis of Survey Date/Social Sciences data.

## Data Acquisition and Preparation

```{r}
load_atus_data <- function(file_base = c("resp", "rost", "act")){
  if(!dir.exists(file.path("data", "mp02"))){
    dir.create(file.path("data", "mp02"), showWarnings=FALSE, recursive=TRUE)
  }
  
  file_base <- match.arg(file_base)
  
  file_name_out <- file.path("data", 
                             "mp02", 
                             glue("atus{file_base}_0324.dat"))
  
  if(!file.exists(file_name_out)){
    
    url_end <- glue("atus{file_base}-0324.zip")
    
    temp_zip <- tempfile(fileext=".zip")
    temp_dir <- tools::file_path_sans_ext(temp_zip)
    
    request("https://www.bls.gov") |>
      req_url_path("tus", "datafiles", url_end) |>
      req_headers(`User-Agent` = "Mozilla/5.0 (Macintosh; Intel Mac OS X 10.15; rv:143.0) Gecko/20100101 Firefox/143.0") |>
      req_perform(temp_zip)
    
    unzip(temp_zip, exdir = temp_dir)
    
    temp_file <- file.path(temp_dir, basename(file_name_out))
    
    file.copy(temp_file, file_name_out)
  }
  
  file <- read_csv(file_name_out, 
                   show_col_types = FALSE)
  
  switch(file_base, 
         resp=file |> 
           mutate(survey_weight = TUFNWGTP, 
                  time_alone = TRTALONE,
                  marriage_status = case_match(TRSPPRES, 1 ~ "Spouse Present", 2 ~ "Unmarried Spouse Present", 3 ~ "None"),
                  employment = case_match(TUABSOT, 1 ~ "Yes", 2 ~ "No", 3 ~ "Retired",4 ~ "Disabled",5 ~ "Unable"),
                  school = case_match(TESCHLVL, 1 ~ "HS", 2 ~ "Uni"),
                  income = TRERNWA,
                  time_alone = TRTALONE,
                  occupation = TRDTOCC1,
                  month = TUMONTH,
                  survey_year = TUYEAR,
                  number_children = TRCHILDNUM),
         
         rost=file |>
           mutate(sex = case_match(TESEX, 1 ~ "M", 2 ~ "F"),
                  individual = TULINENO,
                  age = TEAGE),
         act =file |>
           mutate(activity_n_of_day = TUACTIVITY_N, 
                  time_spent_min = TUACTDUR24, 
                  start_time = TUSTARTTIM,
                  stop_time = TUSTOPTIME, 
                  level1_code = paste0(TRTIER1P, "0000"), 
                  level2_code = paste0(TRTIER2P, "00"),
                  level3_code = TRCODEP,
                  children = TR_03CC57,
                  location = TEWHERE) 
  ) |> 
    rename(participant_id = TUCASEID) |>
    select(matches("[:lower:]", 
                   ignore.case=FALSE))
}

load_atus_activities <- function(){
  if(!dir.exists(file.path("data", "mp02"))){
    dir.create(file.path("data", "mp02"), showWarnings=FALSE, recursive=TRUE)
  }
  
  dest_file <- file.path("data",
                         "mp02",
                         "atus_activity_codes.csv")
  
  if(!file.exists(dest_file)){
    download.file("https://michael-weylandt.com/STA9750/mini/atus_activity_codes.csv", 
                  quiet=TRUE, 
                  destfile=dest_file, 
                  mode="wb")
  }
  
  read_csv(dest_file, show_col_types = FALSE) 
}

```

Reorganizing data tables

```{r}
resp_data <- load_atus_data("resp")

#resp_data = participant id, time alone, survey year, survey weight

rost_data <- load_atus_data("rost")

#rost_data = participant id, sex (household members)

act_data <- load_atus_data("act")

# act_Data = participant id, activity n of day, time spent, start time, stop time, 
#level 1 code, level 2 code, level 3 code

act_code <- load_atus_activities()

#act_code = code level 1-3, task level 1-3

#have three tables for each level of code

codelevel1 <- act_code |>
  select(code_level1, task_level1)

codelevel1 <- codelevel1 |>
  distinct(code_level1, .keep_all = TRUE)

codelevel2 <- act_code |>
  select(code_level2, task_level2)

codelevel2 <- codelevel2 |>
  distinct(code_level2, .keep_all = TRUE)

codelevel3 <- act_code |>
  select(code_level3, task_level3)

codelevel3 <- codelevel3 |>
  distinct(code_level3, .keep_all = TRUE)

#join act_data with codes

act_data_joined <- act_data |>
  left_join(codelevel1, by = c("level1_code" = "code_level1")) |>
  left_join(codelevel2, by = c("level2_code" = "code_level2")) |>
  left_join(codelevel3, by = c("level3_code" = "code_level3"))

full_data <- resp_data |>
  full_join(act_data_joined, by = "participant_id")

full_data <- full_data |>
  mutate(participant_id = as.character(participant_id))

rost_data <- rost_data |>
  mutate(participant_id = as.character(participant_id))

full_data_rost <- full_data |>
  full_join(rost_data, by = "participant_id", relationship = "many-to-many")

```

## Exploratory Analysis

# Task 2 
  
1 Many total hours were recorded on sleeping-type activities? 2241332 hours

```{r}
full_data |>
  filter(str_detect(task_level2,"Sleep")) |>
  summarise(sum_hour = sum(time_spent_min,na.rm = TRUE)/60) |>
  gt() |>
  cols_label(sum_hour = "Total Sleep Hours") |>
  tab_header(title = "Sleep-Type Activities") |>
  cols_align(align = "center") |>
  fmt_number(decimals = 0)
```

2 How many female participants reported spending no time alone in 2003? 104 female participants

```{r}
full_data_rost |>
  select(participant_id,individual,time_alone,sex) |>
  filter(individual == 1,
         time_alone == 0,
         sex == "F") |>
  distinct() |>
  summarise(total_female = n()) |>
  gt() |>
    cols_label(total_female = "Number of Female Participants") |>
    tab_header(title = "Female Participants Who Spent No Time Alone")|>
    cols_align(align = "center") |>
  fmt_number(decimals = 0)

```
  
# Task 3

1 How many children under the age of 18 live in the respondent’s home? 215,155

```{r}
rost_data |>
select(participant_id,age) |>
filter (age <= 18)|>
summarise(age = n()) |>
gt() |>
cols_label(age = "Number of Children") |>
tab_header(title = "Children <18 Living in Respondent Home")|>
cols_align(align = "center") |>
fmt_number(decimals = 0)
```

2 Is the respondent married? 126,381 unmarried

```{r}
resp_data |>
  select(participant_id,marriage_status) |>
  mutate(participant_id = as.character(participant_id),
         marriage_status = if_else(marriage_status == "Spouse Present", "Yes", "No")) |>
  slice_head(n=10) |>
  gt() |>
  cols_label(participant_id = "Participant Id",
             marriage_status = "Marriage Status") |>
  tab_header(title = "Respondent Marriage Status")|>
  cols_align(align = "left")
```

3 What is the respondent’s employment status (employed, unemployed, retired, etc.)?

```{r}
full_data |>
  select(participant_id,employment) |>
  filter(!is.na(employment)) |>
  mutate(employment = case_when(employment == "Yes" ~ "Employed",
                                  employment == "No"  ~ "Unemployed",
                                  TRUE ~ employment)) |>
  slice_head(n=10) |>
  gt() |>
  cols_label(participant_id = "Participant Id",
             employment = "Employment Status") |>
  tab_header(title = "Respondent Employment Status")|>
  cols_align(align = "left")
```

4 Location of activity

```{r}
full_data |>
  select(participant_id,task_level1, location) |>
  filter(location > 0) |>
  slice_head(n=10) |>
  gt() |>
  cols_label(participant_id = "Participant Id",
             task_level1 = "Activity",
             location = "Location") |>
  tab_header(title = "Respondent Activity Location")|>
  cols_align(align = "left")
```

5 Is the respondent enrolled in a college or university (not high school)?

```{r}
full_data |>
  select(participant_id,school) |>
  filter(!is.na(school)) |>
  slice_head(n=10) |>
  gt() |>
  cols_label(participant_id = "Participant Id",
             school = "School") |>
  tab_header(title = "Respondent School")|>
  cols_align(align = "left")

```

# Task 4 

1 How many different respondents have answered an ATUS survey since 2003?

```{r}
full_data |>
  distinct(participant_id) |>
  summarize(total = n()) |>
  gt() |>
  cols_label(total = "Number of Respondents") |>
  tab_header(title = "Number of Different Respondents") |>
  cols_align(align = "center") |>
  fmt_number(decimals = 0)

```

2 Americans enjoy watching a variety of sports. How many different sports does ATUS ask about watching as a “Level 3” task?  

```{r}
full_data |>
  select(task_level1,task_level3) |>
  filter(str_detect(task_level1,"Sports") &
           str_detect(task_level3, "Watch")) |>
  distinct() |>
  summarize(total = n()) |>
  gt() |>
  cols_label(total = "Number of Sports") |>
  tab_header(title = "Different Sports ATUS Has For Watching") |>
  cols_align(align = "center")

```

3 Approximately what percent of Americans are retired?  

```{r}
full_data |> 
  select(survey_weight,employment) |>
  distinct() |>
  summarize(total = sum(survey_weight, na.rm = TRUE),
              retired_population = sum(survey_weight[str_detect(employment, "Ret")],na.rm = TRUE)) |>
  mutate(percentage = round((retired_population / total), 4),
         percentage = paste0(percentage, "%")) |>
  select(percentage) |>
  gt() |>
  cols_label(percentage = "Percentage of Retired Americans") |>
  tab_header(title = "Percent of Americans That Are Retired") |>
  cols_align(align = "center")|>
  fmt_number(columns = percentage,
             decimals = 0,
             suffixing = " %" )

```

4 On average, how many hours do Americans sleep per night?

```{r}
full_data |>
  select(time_spent_min,task_level3,survey_weight) |>
  filter(str_detect(task_level3, "Sleep")) |>
  summarize(avg_time_sleep = weighted.mean(time_spent_min, survey_weight)) |>
  mutate(avg_time_sleep_hours = avg_time_sleep/60) |>
  select (avg_time_sleep_hours) |>
  gt() |>
  cols_label(avg_time_sleep_hours = "Hours of Sleep") |>
  tab_header(title = "Average Hours of Sleep Americans Get") |>
  cols_align(align = "center") |>
  fmt_number(columns = avg_time_sleep_hours,
             decimals = 2)

```

5 On average, how many hours do Americans with one or more children in the home spend taking care of their children (all activities including healthcare and involvement in their children’s education)?


```{r}
full_data_rost |>
  select(children,time_spent_min,task_level2,survey_weight,number_children,individual) |>
  filter(number_children > 0,
         str_detect(task_level2,"hildren"),
         individual == 1) |>
  summarize(avg_time_children = weighted.mean(time_spent_min, survey_weight[str_detect(task_level2,"hildren")],na.rm = TRUE)/60) |>
  gt() |>
  cols_label(avg_time_children = "Hours Spent With Children") |>
  tab_header(title = "Average Hours of Time Americans Spend On Their Children") |>
  cols_align(align = "center") |>
  fmt_number(columns = avg_time_children,
             decimals = 4)

```

# Task 5 















## Final Insights and Deliverable

Code related to the final deliverable of the assignment goes here. 



------------------------------------------------------------------------

This work ©2025 by jackeee101 was initially prepared as a Mini-Project for
STA 9750 at Baruch College. More details about this course can be found at
[the course site](https://michael-weylandt.com/STA9750) and instructions for
this assignment can be found at 
[MP #02](https://michael-weylandt.com/STA9750/mini/mini02.html)
